rejected_text

### 2024-10-04 paper/rejected-text.qmd
Updates including Lucias comments

@@

>>>>

Second.5. the discusison of self-sorting: single parents provide more care and hence may be more likely to choose, if they are able, more accessible neighbourhoods than the rest of the population in the same household income grouping. In a Canadian and U.S. context, households with children may locate to catchments with 'better' schools, often more suburban with lower potential access scores overall. Furthermore, statistics show that in the last years, the number of single parents families in Canada has increased. In 2022, there were about 1.84 million single parents compared to about 1.56 million in 2010 and 1,3 million in 2001 (https://www.statista.com/statistics/443342/single-parent-families-in-canada/ & https://www.justice.gc.ca/eng/rp-pr/jr/jr12/p5a.html#ftn4). Furthermore, Ontario is the Canadian province where most of the lone parent families live (749,769 families, https://www.statista.com/statistics/446667/lone-parent-families-in-canada-by-province/). Most lone-families are headed by female-lone parent. (AS TO ADD IN HAMILTON SPECIFIC NUMBERS)

@@

Even if we are on the right direction to develop human-centred urban areas by facilitating caring activities, the chrono-urbanism needs to set the ground on aspects that specifically target caring activities, given the multiple impacts it has on everyday mobility, the unequal distribution of tasks among the population and its related socioeconomic consequences.

The process of gentrification and displacement are trends also occurring in Hamilton. On the horizon of rising rents, there is a risk of displacement among more vulnerable households, who may be replaced by individuals with higher incomes who can afford different transport modes, with more flexible schedules and are more likely to use ICT arrangements (including telework, e-shopping, and other online services). While, lower income households may be particularly vulnerable to locating in areas with worse accessibility to care alternatives, which could have negative consequences for these households and for the society as a whole.

Even if we are on the right direction to develop human-centred urban areas by facilitating caring activities, the chrono-urbanism needs to set the ground on aspects that specifically target caring activities, given the multiple impacts it has on everyday mobility, the unequal distribution of tasks among the population and its related socioeconomic consequences. Therefore, it is necessary to provide alternatives to measure progress on this important issue. City planning should respond to these issues to promote equity. On the other hand, an intersectional approach to understand how different personal identities interact in our daily day activities in the cities is necessary.

Even if we are on the right direction to develop human-centred urban areas by facilitating caring activities, the chrono-urbanism needs to set the ground on aspects that specifically target caring activities, given the multiple impacts it has on everyday mobility, the unequal distribution of tasks among the population and its related socioeconomic consequences.
Therefore, it is necessary to provide alternatives to measure progress on this important issue.
This work leaves many doors open for further research. For example,
•	the role that gender plays in these households.
•	Job arrangements per type of household. Some studies observe that working from home arrangements are more likely available for higher education attainment households (likely to have higher income), and families with children, but also living in neighbourhoods with good accessibility,
•	Finally, an intersectional approach to understand how our personal identities interact in our access to essential activities and caring services.
City planning should respond to these issues to promote equity. On the other hand, an intersectional approach to understand how different personal identities interact in our daily day activities in the cities is necessary.

As in other case studies, essential opportunities and services tend to concentrate on Hamilton central. Therefore, it is more likely to carry out daily activities, including caring ones, in this area using sustainable modes such as walking or biking.

However, this study highlights that there seems to be a spatial mismatch between dwelling availability, family profile and eventually (housing and mobility) affordability. At the neighbourhood level, the concentration of opportunities for all category types is in Hamilton Central, but households with children may not live there.

Richer families may concentrate in either neighborhoods classified with poor accessibility: either “Somewhat caring and not complete” or “Not caring and not complete. However, these families are likely to have different mobility alternatives available. The literature shows that higher income households have a lower mobility share compared to lower income households. Furthermore, they are more likely to be assisted by different service arrangements (i.e. e-shopping, service deliveries, taxis and MaaS services, working from home arrangements,,…).

Our results show a different story for low-income households.  If they can afford it, these households will prefer to live in very caring and very complete neighbourhoods, which will ease their accessibility to daily activities and essential services and therefore, avoiding social exclusion. In this respect, one-parent families are more likely to be time poor. For them, living in low access/incomplete suburbs increases their chancesof  falling into social exclusion. Furthermore, school closures or any other type of relocation of essential services puts more pressure on their shoulders.
